Quantum Interval-Valued Probability: Measurement and Probability

### 2017-10-15 prop_iop.tex
prop_iop.tex \subsection{Category Theory} Adding...

>>>>

\subsection{Category Theory}

It looks like $\iota$ might be a morphism in a category. Let's try
to check if it is true here.

\begin{definition}Given $\mathscr{I}$ is a collection of intervals,
we say a interval-valued function\nb$\iota:\mathscr{I}'\rightarrow\mathscr{I}''$
is additive if $\iota$ satisfies the following properties. 
\begin{itemize}
\item $\iota\left(\imposs\right)=\imposs$. 
\item $\iota\left(\necess\right)=\necess$. 
\item For any $\left[\ell,r\right]\in\mathscr{I}'$, $\iota\left(\necess-\left[\ell,r\right]\right)=\necess-\iota\left(\left[\ell,r\right]\right)$. 
\item For a pair\nb$\left[\ell_{0},r_{0}\right]$ and $\left[\ell_{1},r_{1}\right]\in\mathscr{I}'$,
if $\left[\ell_{0},r_{0}\right]\subseteq\left[\ell_{1},r_{1}\right]$,
then $\iota\left(\left[\ell_{0},r_{0}\right]\right)\subseteq\iota\left(\left[\ell_{1},r_{1}\right]\right)$. 
\item For a pair\nb$\left[\ell_{0},r_{0}\right]$ and $\left[\ell_{1},r_{1}\right]\in\mathscr{I}'$,
if $\left[\ell_{0},r_{0}\right]+\left[\ell_{1},r_{1}\right]\cap\left[0,1\right]\neq\emptyset$,
then $\left[\ell_{0},r_{0}\right]+\left[\ell_{1},r_{1}\right]\in\mathscr{I}'$
and $\iota\left(\left[\ell_{0},r_{0}\right]+\left[\ell_{1},r_{1}\right]\right)\subseteq\iota\left(\left[\ell_{0},r_{0}\right]\right)+\iota\left(\left[\ell_{1},r_{1}\right]\right)$. 
\end{itemize}
Moreover, $\iota$ is called convex if for any three intervals\nb$\left[\ell_{0},r_{0}\right]$,
$\left[\ell_{1},r_{1}\right]$, and $\left[\ell_{2},r_{2}\right]\in\mathscr{I}'$,
their sum $\left[\ell_{0},r_{0}\right]+\left[\ell_{1},r_{1}\right]+\left[\ell_{2},r_{2}\right]\in\mathscr{I}'$
implies $\iota\left(\left[\ell_{0},r_{0}\right]+\left[\ell_{1},r_{1}\right]+\left[\ell_{2},r_{2}\right]\right)+\iota\left(\left[\ell_{2},r_{2}\right]\right)\subseteq\iota\left(\left[\ell_{0},r_{0}\right]+\left[\ell_{2},r_{2}\right]\right)+\iota\left(\left[\ell_{1},r_{1}\right]+\left[\ell_{2},r_{2}\right]\right)$.\end{definition}

\begin{lemma}\label{lemma:interval2interval}Consider an additive
interval-valued function\nb$\iota:\mathscr{I}'\rightarrow\mathscr{I}''$.
Then, given a QIVPM\nb$\bar{\mu}':\events\rightarrow\mathscr{I}'$,
a function\nb$\bar{\mu}'':\events\rightarrow\mathscr{I}''$ defined
by $\bar{\mu}''\left(P\right)=\iota\left(\bar{\mu}'\left(P\right)\right)$
is a QIVPM.\end{lemma}

\begin{proof}~
\begin{itemize}
\item $\bar{\mu}''\left(\mathbb{0}\right)=\iota\left(\bar{\mu}'\left(\mathbb{0}\right)\right)=\iota\left(\imposs\right)=\imposs$.
\item $\bar{\mu}''\left(\mathbb{1}\right)=\iota\left(\bar{\mu}'\left(\mathbb{1}\right)\right)=\iota\left(\necess\right)=\necess$.
\item For any projection $P$, $\bar{\mu}''\left(\mathbb{1}-P\right)=\iota\left(\necess-\bar{\mu}'\left(P\right)\right)=\necess-\bar{\mu}''\left(P\right)$.
\item For a pair of mutually orthogonal projections\nb$P_{0}$ and $P_{1}\in\events$,
since $\emptyset\neq\bar{\mu}'\left(P_{0}+P_{1}\right)\cap\left[0,1\right]\subseteq\bar{\mu}'\left(P_{0}\right)+\bar{\mu}'\left(P_{1}\right)\cap\left[0,1\right]$,
we have $\bar{\mu}'\left(P_{0}\right)+\bar{\mu}'\left(P_{1}\right)\in\mathscr{I}'$
and
\[
\bar{\mu}''\left(P_{0}+P_{1}\right)=\iota\left(\bar{\mu}'\left(P_{0}+P_{1}\right)\right)\subseteq\iota\left(\bar{\mu}'\left(P_{0}\right)+\bar{\mu}'\left(P_{1}\right)\right)\subseteq\iota\left(\bar{\mu}'\left(P_{0}\right)\right)+\iota\left(\bar{\mu}'\left(P_{1}\right)\right)=\bar{\mu}''\left(P_{0}\right)+\bar{\mu}''\left(P_{1}\right)\,.
\]
\end{itemize}
\end{proof}
